TRITON: Texture Recovering Image Translation Network [[TODO Make catchier]]

### 2022-05-16 paper.tex
Added new abstract

\begin{abstract}
	Image translation has been succesful in improving benchmarks in robotic reinforcement learning.
	Current unpaired sim to real image translation algorithms are not globally temporally consistent. 
	These techniques do not leverage the latent 3d geometry that creates the input images.
	Much of the content in photographs can be approximated as albedo maps on the surfaces of 3d objects.
	In this paper, we combine differentiable rendering with image translation to recover the textures of 3d objects.
	This algorithm takes advantage of the input geometry by projecting learnable textures onto their surfaces, before feeding it into an image translation algorithm.
	With the addition of certain losses, we achieve temporal consistency without using temporal queues (such as optical flow etc...reword this sentence?).
	Previous algorithms that have tried to perform unpaired image translation using neural textures have been limited to camera movements.
	In contrast, this algorithm can handle the movements of objects in the scene, which is useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the accuracy of the translations with respect to ground truth photographs is improved by this approach.
\end{abstract}

>>>>

\begin{abstract}
	Unpaired image translation algorithms can be used for sim-to-real tasks, but they often fail to generate temporally consistent results.
	Because of this, the details or even identity of a particular object might change as it moves across a scene.
	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
	Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
	These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly [[ie. no need for optical flow]].
	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
\end{abstract}
